A multi-species benchmark for training and validating mass spectrometry proteomics machine learning models

### 2024-10-01 doc/nine-species/nine-species.tex

\begin{table}
  \centering
  \scriptsize
\begin{tabular}{lllrrrrrrrrrr}
\hline
PRIDE & Species & UniProt & Files & Spectra &
\multicolumn{2}{c}{Main} & \multicolumn{2}{c}{Balanced} & Pre & Frag \\
& & & & & PSM & Pep  & PSM & Pep  \\
\hline
PXD005025 & \textit{Vigna mungo} & UP000087766 & 24 & 932,848 &
108,402 & 11,638 & 102,255 & 11,557
& 20 & 0.05 \\
PXD004948 & \textit{Mus musculus} & UP000000589 & 13 & 306,786 & 
25,522 & 5630 & 25,522 & 5630
& 10 & 0.05 \\
PXD004325 & \textit{Methanosarcina mazei} & UP000033058  & 72 & 3,728,183 &
267,183 & 15,220 & 100,485 & 11,934
& 10 & 0.05 \\
PXD004565 & \textit{Bacillus subtilis} & UP000001570 & 106 & 4,336,428 &
1,351,938 & 28,364 & 113,234 & 17,481
& 30 & 0.05 \\
PXD004536 & \textit{Candidatus endoloripes} & UP000094849 & 11 & 2,272,023 &
82,514 & 8080 & 82,514 & 8080
& 20 & 0.05 \\
PXD004947 & \textit{Solanum lycopersicum} & UP000004994 & 60 & 603,506 &
177,553 & 48,459 & 100,056 & 35,787
& 15 & 0.05 \\
PXD003868 & \textit{Saccharomyces-cerevisiae} & UP000002311 & 27 & 1,477,397 &
585,846 & 19,102 & 108,973 & 13,285
& 20 & 0.05 \\
PXD004467 & \textit{Apis mellifera} & UP000005203 & 17 & 823,169 &
194,604 & 21,081 & 102,285 & 18,630
& 20 & 0.05 \\
PXD004424 & \textit{H.\ sapiens} & UP000005640 & 26 & 684,821 &
44,555 & 10,848 & 44,555 & 10,848
& 20 & 0.02 \\
\hline
Total & & & 343 & 15,165,161  & 2,838,117 & 168,422 & 779,879 & 133,232 \\
\end{tabular}
\caption{{\bf Two versions of the nine-species benchmark.}
  Counts of the number of annotated spectra and distinct peptide sequences are provided for the main and balanced versions of the benchmark.
The final two columns specify the precursor window size (in ppm) and fragment bin size (in Da) used in the database search step.
}
\label{tab:benchmark}
\end{table}

@@

The dataset contains files resulting from various steps in the generation of the benchmark:
\begin{itemize}
\item Spectrum files in MGF format, produced by ThermoRawFileParser.
\item Reference proteome files in FASTA format, downloaded from UniProt.
\item Search results files for both targets and decoys, in tab-delimited format, produced by Tide.
\item PSM-level Percolator results files for targets, in tab-delimited format.
`\item Annotated MGF and corresponding mzSpecLib \cite{klein2024proteomics} files for both versions of the benchmark (main and balanced).
\end{itemize}
Also included are log files for the steps of the analysis pipeline carried out using Crux \cite{park2008rapid} (Tide indexing, Tide search, and Percolator).
The data is available at \url{https://doi.org/10.5281/zenodo.12819175}.

>>>>

\begin{table}
  \centering
  \scriptsize
\begin{tabular}{lllrrrrrrrrrr}
\hline
PRIDE & Species & UniProt & Files & Spectra &
\multicolumn{2}{c}{Main} & \multicolumn{2}{c}{Balanced} & Pre & Frag \\
& & & & & PSM & Pep  & PSM & Pep  \\
\hline
PXD005025 \cite{paiva2016label} & \textit{Vigna mungo} & UP000087766 & 24 & 932,848 &
\edit{108,402} & \edit{11,638} & \edit{102,255} & \edit{11,557}
& 20 & 0.05 \\
PXD004948 \cite{nevo2017impact} & \textit{Mus musculus} & UP000000589 & 13 & 306,786 & 
\edit{25,522} & \edit{5630} & \edit{25,522} & \edit{5630}
& 10 & 0.05 \\
PXD004325 \cite{cassidy2016combination} & \textit{Methanosarcina mazei} & UP000033058  & 72 & 3,728,183 &
\edit{267,183} & \edit{15,220} & \edit{100,485} & \edit{11,934}
& 10 & 0.05 \\
PXD004565 \cite{reuss2017large} & \textit{Bacillus subtilis} & UP000001570 & 106 & 4,336,428 &
\edit{1,351,938} & \edit{28,364} & \edit{113,234} & \edit{17,481}
& 30 & 0.05 \\
PXD004536 \cite{petersen2016chemosynthetic} & \textit{Candidatus endoloripes} & UP000094849 & 11 & 2,272,023 &
\edit{82,514} & \edit{8080} & \edit{82,514} & \edit{8080}
& 20 & 0.05 \\
PXD004947 \cite{mata2017depth} & \textit{Solanum lycopersicum} & UP000004994 & 60 & 603,506 &
\edit{177,553} & \edit{48,459} & \edit{100,056} & \edit{35,787}
& 15 & 0.05 \\
PXD003868 \cite{seidel2017quantitative} & \textit{Saccharomyces-cerevisiae} & UP000002311 & 27 & 1,477,397 &
\edit{585,846} & \edit{19,102} & \edit{108,973} & \edit{13,285}
& 20 & 0.05 \\
PXD004467 \cite{hu2016proteome} & \textit{Apis mellifera} & UP000005203 & 17 & 823,169 &
\edit{194,604} & \edit{21,081} & \edit{102,285} & \edit{18,630}
& 20 & 0.05 \\
PXD004424 \cite{cypryk2017proteomic} & \textit{H.\ sapiens} & UP000005640 & 26 & 684,821 &
\edit{44,555} & \edit{10,848} & \edit{44,555} & \edit{10,848}
& 20 & 0.02 \\
\hline
Total & & & 343 & 15,165,161  & 2,838,117 & 168,422 & 779,879 & 133,232 \\
\end{tabular}
\caption{{\bf Two versions of the nine-species benchmark.}
  Counts of the number of annotated spectra and distinct peptide sequences are provided for the main and balanced versions of the benchmark.
The final two columns specify the precursor window size (in ppm) and fragment bin size (in Da) used in the database search step.
}
\label{tab:benchmark}
\end{table}

@@

The dataset \cite{noble2024benchmark} contains files resulting from various steps in the generation of the benchmark:
\begin{itemize}
\item Spectrum files in MGF format, produced by ThermoRawFileParser.
\item Reference proteome files in FASTA format, downloaded from UniProt.
\item Search results files for both targets and decoys, in tab-delimited format, produced by Tide.
\item PSM-level Percolator results files for targets, in tab-delimited format.
`\item Annotated MGF and corresponding mzSpecLib \cite{klein2024proteomics} files for both versions of the benchmark (main and balanced).
\end{itemize}
Also included are log files for the steps of the analysis pipeline carried out using Crux \cite{park2008rapid} (Tide indexing, Tide search, and Percolator).
The data \cite{noble2024benchmark} is available at \url{https://doi.org/10.5281/zenodo.13685813}.
